---
title: "Abdul Naji Chapter 3"
author: "Abdul Naji"
date: "4/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 3.2.4 Exercises

Run ggplot(data = mpg). What do you see?

How many rows are in mpg? How many columns?

What does the drv variable describe? Read the help for ?mpg to find out.

Make a scatterplot of hwy vs cyl.

What happens if you make a scatterplot of class vs drv? Why is the plot not useful?

```{r}
library(tidyverse)
```

```{r}
ggplot(data = mpg)
```

#Nothing shows up because we haven't told R what to graph

```{r}
dim(mpg)
```

#There are 234 rows and 11 columns

```{r}
?mpg
```

#drv is whether the car is a front wheel, rear wheel or 4 wheel drive

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = cyl, y = hwy))
```

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = class, y = drv))
```

#The graph isn't telling us anything because both of these variables are categorical. Both are meant to be on the x axis

#3.3.1 Exercises
What’s gone wrong with this code? Why are the points not blue?

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))


Which variables in mpg are categorical? Which variables are continuous? (Hint: type ?mpg to read the documentation for the dataset). How can you see this information when you run mpg?

Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?

What happens if you map the same variable to multiple aesthetics?

What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)

What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)? Note, you’ll also need to specify x and y.

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
```

#The points aren't blue because it was put into the aes() rather than outside of it.

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```

```{r}
?mpg
```

```{r}
str(mpg)
```

#manufacturer, model, trans, drv, fl and class are categorical.

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, color = displ))
```

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, size = displ))
```

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, color = drv, shape = drv))
```

#The same variablecan be mapped to multiple aesthetics as long as they are compatible with the variable.

```{r}
?geom_point(stroke)
```

#Stroke works with certain shapes, 21-24, we can use it to fill and give color to the points

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy), shape = 21, fill = 'blue', size = 3, stroke = 3, color = 'yellow')
```

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, color = displ < 5))
```

#Creates a scatterplot and color codes the true and false.

#Exercises 3.5.1
What happens if you facet on a continuous variable?

What do the empty cells in plot with facet_grid(drv ~ cyl) mean? How do they relate to this plot?

What plots does the following code make? What does . do?

Take the first faceted plot in this section:
What are the advantages to using faceting instead of the colour aesthetic? What are the disadvantages? How might the balance change if you had a larger dataset?

Read ?facet_wrap. What does nrow do? What does ncol do? What other options control the layout of the individual panels? Why doesn’t facet_grid() have nrow and ncol arguments?

When using facet_grid() you should usually put the variable with more unique levels in the columns. Why?

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy)) + facet_wrap(~ cty, nrow = 2)
```

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y= hwy)) + facet_grid(drv ~ cyl)
```

#The empty plots mean those pairs do not exist.

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y= hwy)) + facet_grid(drv ~ .)
```

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy)) + facet_grid(. ~ cyl)
```

#drv is the rows and cyl is the columns.

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy)) + facet_wrap(~ class, nrow = 2)
```

#Too many colors can be confusing, but having them on separate plots can also cause confusion when making comparisons.

#5 – Read ?facet_wrap. What does nrow do? What does ncol do? What other options control the layout of the individual panels? Why doesn’t facet_grid() have nrow and ncol argument?

#nrow and ncol tell us how many rows and columns. Facet grid doesn't have them because since they are equal to the number of levels in the variable.

#When using facet_grid() you should usually put the variable with more unique levels in the columns. Why?

#The dependent variables are put on the y axis so it's easier to see the trends.


#3.6.1 Exercies

#What geom would you use to draw a line chart? A boxplot? A histogram? An area chart?

#geom_line(), geom_boxplot(), geom_histogram(), geom_area() 

#Run this code in your head and predict what the output will look like. Then, run the code in R and check your predictions.

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + geom_point() + geom_smooth(se = FALSE)
```

#What does show.legend = FALSE do? What happens if you remove it? Why do you think I used it earlier in the chapter?

#Making is false will hide the legend and leaving it true will show it. It was probably used to hide the legend.

#What does the se argument to geom_smooth() do?

#It allows the confidence interval around the smooth curve to either be shown or hidden.

#Will these two graphs look different? Why/why not? 
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth()

ggplot() + 
  geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))

#They will look the same.

#Recreate the R code necessary to generate the following graphs.

```{r}
ggplot(data = mpg, mapping = aes(y = hwy, x = displ)) + geom_point() + geom_smooth(se = FALSE)
```

```{r}
ggplot(data = mpg, mapping = aes(y = hwy, x = displ)) + geom_point() + geom_smooth(mapping = aes(group = drv), se = FALSE, show.legend = FALSE)
```

```{r}
ggplot(data = mpg, mapping = aes(y = hwy, x = displ)) + geom_point(mapping = aes(color = drv)) + geom_smooth(mapping = aes(color = drv, group = drv), se = FALSE)
```

```{r}
ggplot(data = mpg, mapping = aes(y = hwy, x = displ)) +  geom_point(mapping = aes(color = drv)) + geom_smooth(se = FALSE)
```

```{r}
ggplot(data = mpg, mapping = aes(y = hwy, x = displ)) + geom_point(mapping = aes(color = drv)) + geom_smooth(mapping = aes(linetype = drv), se = FALSE)
```

```{r}
ggplot(data = mpg, mapping = aes(y = hwy, x = displ)) + geom_point(mapping = aes(fill = drv), color = 'white', stroke = 2, shape = 21)
```

#Exercises 3.7.1

#What is the default geom associated with stat_summary()? How could you rewrite the previous plot to use that geom function instead of the stat function?

```{r}
diamonds %>% group_by(cut) %>% summarize(median_y = median(depth),
                                         min_y = min(depth),
                                         max_y = max(depth)) %>%
  ggplot() +
  geom_pointrange(mapping = aes(x = cut, y = median_y, ymin = min_y, ymax = max_y)) +
  labs(y = 'depth')
```

#What does geom_col() do? How is it different to geom_bar()?

#geom_bar() does the frequencies automatically while the geom_col() the frequencies are counted manually.

#What variables does stat_smooth() compute? What parameters control its behaviour?

#The method argument defines the smotthing method and which variables to compute. n, span, full range and level control the behavior.

#In our proportion bar chart, we need to set group = 1. Why? In other words what is the problem with these two graphs?

```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, y = ..prop..))
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, fill = color, y = ..prop..))
```

#group = 1 is used to specify the frequencies between each variable, otherwise all will be filled up since the proportion within each is 1, and we won't have a good graph with the information we want.













